### 2013-06-11 context-dependence.tex
.

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth]{tasep/all-mcmc-runs}
  \end{center}
  \caption{ Results from MCMC estimates of the parameter in TASEP (mutation rate multiplied by time).  
  Vertical line shows the true value.
  }
\end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth,page=1]{ising/all-mcmc-runs}
  \end{center}
  \caption{ Results from MCMC estimates of the mutation rate parameter in the Ising model (scaled by amount of time). 
  Vertical line shows the true value.
  }
\end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth,page=3]{ising/all-mcmc-runs}
  \end{center}
  \caption{ Results from MCMC estimates of the magenization parameter in the Ising model. 
  Vertical line shows the true value.
  }
\end{figure}

>>>>

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth]{tasep/all-mcmc-runs}
  \end{center}
  \caption{ Results from MCMC estimates for six different data sets of the parameter in TASEP (mutation rate multiplied by time).  
  Vertical line shows the true value.
  }
\end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth,page=1]{ising/all-mcmc-runs}
  \end{center}
  \caption{ Results from MCMC estimates of the time-scaled mutation rate parameter $\lambda t$,
  in ten different simulated datasets under the Ising model.
  Vertical line shows the true value.
  }
\end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth,page=3]{ising/all-mcmc-runs}
  \end{center}
  \caption{ Results from MCMC estimates of the magnetization parameter $\beta$ in the Ising model. 
  Vertical line shows the true value.
  }
\end{figure}

%%%
\subsection{CpG mutation}

Nucleotide sequences of length $10^6$ were simulated with various
